Structured Versus Decorated Cospans

### 2020-12-14 cospans.tex
changes to Thm. 3.1, Thm. 3.2 and Lemma 3.3.

\begin{proof}
This was proved in \cite[Theorems~2.3 \& 3.9]{BC}, where all the structures are specified in detail. {\chris grammatical error follows} In fact, the double category structure only requires that $\X$ have pushouts, whereas the symmetric monoidal structure also requires that $\X$ has binary coproducts and an initial object (and thus all finite colimits), and that $\A$ has and $L$ preserves finite coproducts \cite[Theorem~3.2.3]{CourserThesis}.
\end{proof}

The following theorem establishes an isomorphism between structured and decorated cospan double categories under certain conditions.  We denote by $\Rex$ the 2-category of categories with finite colimits, functors preserving finite colimits, and natural transformations.   Recall that for us a category $\C \in \Rex$ comes with a choice of finite colimits, so it gives a cocartesian monoidal category $(\C,+)$; this induces a well-defined 2-functor $\Rex\to\SMC$.

\begin{thm} \label{thm:equiv}
Suppose $\A$ has finite colimits and $F \maps (\A,+) \to (\Cat,\times)$ is a symmetric lax monoidal pseudofunctor. If the corresponding ordinary pseudofunctor %(via the monoidal Grothendieck construction) {\chris SHOULD THIS PARENTHESIS STAY OR NOT?} 
$F\colon \A\to\SMC$ factors through $\Rex$, then the symmetric monoidal double categories $F\lCsp$ of decorated cospans and $_L\lCsp(\inta F)$ of structured cospans are isomorphic, where $L \maps \A \to \inta F$ is a left adjoint of the induced Grothendieck opfibration $U\maps \inta F \to \A$.
\end{thm}

@@

\begin{lem}\label{lem:MonGroth}
There is a 2-equivalence between the 2-categories of monoidal opfibrations and monoidal opindexed categories. If the base is cocartesian monoidal, there is a 2-equivalence between monoidal opfibrations and pseudofunctors into $\MonCat$. 
%Moreover, symmetric monoidal opfibrations are equivalent to symmetric monoidal opindexed categories, and when the base is cocartesian monoidal these also correspond to pseudofunctors into $\SMC$.
\end{lem}

\begin{proof}
This was shown by Moeller and the third author \cite[Theorems~3.13\&4.2]{MV}. In summary, for a cocartesian base $\A$ we have correspondences
\begin{gather}
\textrm{lax monoidal pseudofunctors }F\maps(\A,+)\to(\Cat,\times) \notag\\
\Updownarrow \notag\\
\textrm{monoidal opfibrations }U\maps(\X,\otimes_\X)\to(\A,+) \notag\\
\Updownarrow \notag\\
\textrm{pseudofunctors } \tilde{F} \maps \A\to \MonCat \notag
\end{gather}
The second equivalence was observed earlier by Shulman \cite{Shulman2008}. Moreover, symmetric lax monoidal pseudofunctors correspond to symmetric monoidal opfibrations, and those to pseudofunctors into $\SMC$.

>>>>

\begin{proof}
This was proved in \cite[Theorems~2.3 \& 3.9]{BC}, where all the structures are specified in detail.  In fact, the double category structure only requires that $\X$ have pushouts, whereas the symmetric monoidal structure also requires that $\X$ and $\A$ have finite colimits and that $L$ preserves finite coproducts \cite[Theorem~3.2.3]{CourserThesis}.
\end{proof}

The following theorem establishes an isomorphism between structured and decorated cospan double categories under certain conditions.  Let $\Rex$ be the 2-category of categories with finite colimits, functors preserving finite colimits, and natural transformations.  Let $\SMC$ be the 2-category of symmetric monoidal categories, strong symmetric monoidal functors and natural transformations.   Recall that for us a category $\C \in \Rex$ comes with a choice of finite colimits, so it gives a specific cocartesian monoidal category $(\C,+)$, and this induces a 2-functor $\Rex \to \SMC$.

\begin{thm} \label{thm:equiv}
Suppose $\A$ has finite colimits and $F \maps (\A,+) \to (\Cat,\times)$ is a symmetric lax monoidal pseudofunctor. If the corresponding pseudofunctor $F \maps \A \to \SMC$ factors through $\Rex$, then the symmetric monoidal double categories $F\lCsp$ of decorated cospans and $_L\lCsp(\inta F)$ of structured cospans are isomorphic, where $L \maps \A \to \inta F$ is a left adjoint of the induced Grothendieck opfibration $U\maps \inta F \to \A$.
\end{thm}

@@

\begin{lem}\label{lem:MonGroth}
There is a 2-equivalence between the 2-categories of monoidal opfibrations and monoidal opindexed categories with a fixed base, and if the base is cocartesian monoidal, there is a 2-equivalence between these and pseudofunctors into $\MonCat$.   Similarly there is a 2-equivalence between symmetric monoidal opfibrations and symmetric monoidal opindexed categories with a fixed base, and if the base is cocartesian monoidal also a 2-equivalence between these and pseudofunctors into $\SMC$.   
\end{lem}

\begin{proof}
This was shown by Moeller and the third author \cite[Theorems~3.13 \& 4.2]{MV}. In summary, for a cocartesian base $\A$ we have correspondences
\begin{gather}
\textrm{lax monoidal pseudofunctors }F\maps(\A,+)\to(\Cat,\times) \notag\\
\Updownarrow \notag\\
\textrm{monoidal opfibrations }U\maps(\X,\otimes_\X)\to(\A,+) \notag\\
\Updownarrow \notag\\
\textrm{pseudofunctors } \tilde{F} \maps \A\to \MonCat \notag
\end{gather}
The second equivalence was observed earlier by Shulman \cite{Shulman2008}. Moreover, symmetric lax monoidal pseudofunctors correspond to symmetric monoidal opfibrations, and those to pseudofunctors into $\SMC$.
